Model Search in Relational Domains

### 2016-10-23 contributions.tex
proof-reading all section
Sketch

\item We present an abstract model search algorithm 
%that strictly 
%generalises the Boolean Constraint Propagation (BCP) procedure 
to compute a fixed point over a relational domain.  We propose 
domain-specific decision heuristics that exploit the expressivity 
of the underlying abstract domain to make effective decisions.

\item We present a lifting of the conflict analysis procedure 
to relational abstract domains in order to learn a generalised reason 
for conflicts.

>>>>

\item We present an abstract model search algorithm 
%that strictly 
%generalises the Boolean Constraint Propagation (BCP) procedure 
that computes a fixed-point over a relational domain.  We propose 
domain-specific decision heuristics that exploit the expressivity 
of the underlying abstract domain to make effective decisions.

\item We sketch a lifting of the conflict analysis procedure 
to relational abstract domains in order to learn a generalised reason 
for conflicts.
